---
title: "CEO departures"
author: "Navid Mohseni"
date: "5/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE, 
                      warning = FALSE, message = FALSE, dpi = 180, fig.width = 8,
                      fig.height = 5)
library(knitr)
library(tidyverse)
library(silgelib)
theme_set(theme_plex())
```

Let's build a model for [CEO departures](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-04-27/readme.md). We can build a model to estimate how involuntary departures are changing.

## Explore Data
departures <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-27/departures.csv')

```{r}
departures <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-27/departures.csv')
```

```{r}
departures %>% count(departure_code)

departures %>% 
  filter(departure_code < 9, 
         fyear > 1995, fyear < 2019) %>% 
  mutate(involuntary = if_else(departure_code %in% 3:4, "involuntary", "other")) %>% 
  count(fyear, involuntary) %>% 
  ggplot(aes(fyear, n, color = involuntary)) + 
  geom_line(size = 1.2, alpha = 0.5) + 
  geom_point(size = 2) + 
  geom_smooth(method = "lm", lty = 2) +
  scale_y_continuous(limits = c(0, NA)) + 
  labs(x = NULL, y = "Number of CEO departures", color = NULL)
  
```


```{r}
dept <- departures %>% 
  filter(departure_code < 9, 
         fyear > 1995, fyear < 2019) %>% 
  mutate(involuntary = if_else(departure_code %in% 3:4, "involuntary", "other"))

df <- dept %>% 
  count(fyear, involuntary) %>% 
  pivot_wider(names_from = involuntary, values_from = n)

library(broom)
mod <- glm(cbind(involuntary, other) ~ fyear, data = df, family = "binomial")
tidy(mod, exponentiate = TRUE)
```

Let's use resampling (Bootstrap)

```{r}
library(rsample)

set.seed(123)

ceo_folds <- bootstraps(dept, times = 1e3)
ceo_folds

fit_binom <- function(split) {
  
  df <- analysis(split) %>% 
  count(fyear, involuntary) %>% 
  pivot_wider(names_from = involuntary, values_from = n)
  
  mod <- glm(cbind(involuntary, other) ~ fyear, data = df, family = "binomial")
  tidy(mod, exponentiate = TRUE)
}

```


```{r}
boot_models <- ceo_folds %>% 
  mutate(coef_info = map(splits, fit_binom))
```

```{r}
intervals <- int_pctl(boot_models, coef_info)
boot_models %>% 
  unnest(coef_info) %>% 
  filter(term == "fyear") %>% 
  ggplot(aes(estimate)) + 
  geom_vline(xintercept = 1, lty = 2, color = "gray50", size = 2) + 
  geom_histogram(alpha = 0.8, fill = "midnightblue")

```


